Pipeline systems and infrastructure for the efficient and open processing of Big neuroimaging Data

### 2018-02-27 paper.tex
start to automatic analysis

        \subsection{Debugging and provenance}
        For each dataset processed in a LONI pipeline, there exists a corresponding
provenance (.prov) XML file. The \textit{Provenance Editor}, a standalone
platform-independent application, reads the metadata from the image headers,
extracts relevant provenance information from them and creates the provenance files. 
This data can be modified by the user in the to correct inaccuracies or append
additional details before being saved. During pipeline execution, the provenance
file will be edited by the LONI pipeline to include details on each processing
step, the environment in which the data was processed and tool binaries used. 
    \section{Automatic Analysis}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Dipy}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Make}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Pydiper}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}

>>>>

        \subsection{Debugging and provenance}
        For each dataset processed in a LONI pipeline, there exists a corresponding
provenance (.prov) XML file. The \textit{Provenance Editor}, a standalone
platform-independent application, reads the metadata from the image headers,
extracts relevant provenance information from them and creates the provenance files. 
This data can be modified by the user in the to correct inaccuracies or append
additional details before being saved. During pipeline execution, the provenance
file will be edited by the LONI pipeline to include details on each processing
step, the environment in which the data was processed and tool binaries used.

    \section{Automatic Analysis}
        \subsection{Summary}
        Automatic analysis (aa) is another Matlab-based modular workflow engine,
having started of as a pipelining system for SPM. User may define their pipeline
through a Matlab user script and specify the tasks in addition to their input
and output types through an XML module interface. Modules used in pipelines must
be integrated into aa which can be easily accomplished through XML interfaces. It is also possible to easily
parallelize the code in qsub, if required. 
        \subsection{Pipeline description}
        aa pipelines have two main components: 1) the Matlab user script and 2)
the XML tasklist. The user script is a script that defines which data will be
processed, any necessary parameter, and how it will be processed. aa provides an example user script,
which can be modified to meet user's needs. The entire pipeline in aa is defined
in a single structure, known as aap, which makes the task of record-keeping
simple.

        The XML tasklist is an ordered list of all the modules that will be applied to
the data, that is read by the user script. This list does not specify any
dependencies as those dependendecies can be inferred by the pipeline through
analysis of the module interfaces. Modules can be separated into two
sections: initialization and main. Modules listed in the initialization section
are to be executed for every task. Conversely, those modules liste in the main
section are only executed once for every task, unless otherwise specified.

        In order to ensure that the correct output data is being operated on,
each task is provided with its own unique folder. The aa engine will ensure that
the necessary input data is located in the folder before task execution and also
acquiring the outputs after task completion.

        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Dipy}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Make}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance}
    \section{Pydiper}
        \subsection{Summary}
        \subsection{Pipeline description}
        \subsection{Pipeline execution}
        \subsection{Debugging and provenance} 
    \section{Use of containers in Workflow engines} 
        \subsection{use of containers in nipype, psom, spm}
